---
title: "Ordinal Regression: ING-IN' across diff Tweeter genders"
output: html_document
---

###Prelims
```{r libraries,echo=FALSE,warning=FALSE,message=FALSE}
#tidyup
library(dplyr)
library(magrittr)
#viz
library(ggplot2)
gendPalette<- c( "#f1a340","#998ec3")
#stats
#library(BayesFactor)
library(ordinal)
library(rstan)
library(brms)


source('helpers.R')
source('stan_utility.R')
```

### What is the data?
From an experiment in which ~300 people saw one 'Tweet' each.

- Four conditions in all:

    - Two gender conditions ('The Tweeter is male/female')
    - Two (ING) conditions: Tweeter uses either *walkin'* or *walking*


#### Get data and tidy it 
(nb, this data has already been tidied up a bunch - eg participants excluded where necessary. This notebook is really just for BRMS tute)
```{r data_proc}
ingin.gender <- read.csv('ing_gender.csv')

#Tidy up (make factors factors, rename cols for transparency)
cols <- 5:17 #cols to be factors
ingin.gender %<>% rename(participant_gender = gender, 
                 tweeter_gender = user_gender, 
                 participant_education = education, 
                 socialmeda_usage = socialmedia, 
                 participant_age = age) %>%
                 mutate_at(cols, factor) %>%
                 dplyr::filter(participant_gender != 'Other') #iltering as so few (2) responses

ingin.gender$grammar <- as.factor(ingin.gender$grammar) #oops forgot him
```

*A note on variable names and scales... the ends of the Likert items are pseudorandomized - such that in some cases, 1 represents the highest extent of the attribute, and in others, 7 does. E.g., for masculinity and femininity, most masculine/feminine = 1, least masculine/feminine = 7. The variables are named to reflect this: the first part of the variable name reflects the left side of the scale (1) and the second part, the right side (7).*


### Ordinal regression models with `fem_not` and `masc_not` as response variables

These are the frequentist ordinal regression models using `clm`.

```{r frequentist_ordeinal regression}
fem.gend.mod <- clm(factor(fem_not) ~ stim*tweeter_gender*participant_gender,  data = ingin.gender)
summary(fem.gend.mod)

masc.gend.mod <- clm(masc_not ~ stim*tweeter_gender*participant_gender,  data = ingin.gender)
summary(masc.gend.mod)
```
Unsurpisingly: if particpants are told the Tweeter is a male, then they are considered much less feminine than if participants are told the Tweeter is a female (duh), and vice versa (duh).

More suprising is in the interaction between participant gender and tweeter gender for femininity (marginal interaction for masculinity). See plot below (but be wary as I'm plotting means which technically I shouldn't really be doing).


###viz this
```{r plots, echo=FALSE}
ingin.gender$fem_not_int <- as.integer(ingin.gender$fem_not)
fem_plot <- ingin.gender %>%
  group_by(participant_gender, tweeter_gender) %>%
  summarise(mean_fem_not_int = mean(fem_not_int), CI.Low = ci.low(fem_not_int), CI.High = ci.high(fem_not_int)) %>%
  mutate(YMin = mean_fem_not_int - CI.Low, YMax = mean_fem_not_int + CI.High) %>%
  ggplot(aes(x=participant_gender,y=mean_fem_not_int, fill=factor(tweeter_gender))) +
  geom_bar(stat ='identity', position="dodge") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25, position=position_dodge(width=0.9))+
  xlab("Participant gender") +
  ylab("Feminine -> Not feminine") +
  scale_fill_manual(values=gendPalette, name = "Tweeter gender", labels = c("Female", "Male"))
fem_plot

```

### Ordinal regression with brms

```{r brms_models, cache=TRUE}
  # BRMS expects ordinal scales to be coded as integers
  ingin.gender$fem_not_int = as.integer(ingin.gender$fem_not)

  # estimate Bayesian ordinal regression model
  fem.gend.bmod <- brm(
    formula =fem_not_int ~ stim*tweeter_gender*participant_gender,
    data = ingin.gender,
    family = cumulative("probit") # proper distribution for likert scales
  )
  
  # run model checks
  check_all_diagnostics(fem.gend.bmod$fit)
  
  # plot parameter distributions
  stanplot(fem.gend.bmod, type="hist")
  
  # posterior predictive check
  pp_check(fem.gend.bmod, nsamples=100, type="bars")
  
  #display summary
  summary(fem.gend.bmod)
  
  ## repeat all steps for model predicting "masc_not"
  ingin.gender$masc_not_int = as.integer(ingin.gender$masc_not)

  masc.gend.bmod <- brm(
    formula =masc_not_int ~ stim*tweeter_gender*participant_gender,
    data = ingin.gender,
    family = cumulative("probit")
  )  
  check_all_diagnostics(masc.gend.bmod$fit)
  stanplot(masc.gend.bmod, type="hist")
  pp_check(masc.gend.bmod, nsamples=100, type="bars")
  summary(masc.gend.bmod)

```
